Observation of the Torsional Motion of a Solar Jet at the Limb

### 2016-08-18 paper/ms_temp_paper.tex
More tweaks

fig = plt.figure(figsize=texfigure.figsize(pytex, figure_width_context='columnwidth'))
plt.imshow(np.rot90(data[2])[::-1, 100:], cmap='viridis', aspect='auto', origin='lower', norm=norm)
plt.colorbar()
plt.xlabel('Time in SST cadence (7.7 s)')
plt.ylabel('Distance along the slit')
sst_slit_fig = manager.save_figure('sst-slit', fig)
sst_slit_fig.figure_env_name = r'figure*'
sst_slit_fig.figure_width = r'\columnwidth'
sst_slit_fig.placement = 't'
sst_slit_fig.caption = r'CRISP/SST H$\alpha$ core line slit analysis.'

@@

dops = np.zeros((len(dop_files), 331, 120)
for i, afile in enumerate(dop_files):
    dops[i] = np.load(afile)

@@

fig, ax = plt.subplots(figsize=texfigure.figsize(pytex, figure_width_context='columnwidth', reference='temp-slit'))
% temp_slit = texfigure.Figure(fig, reference='temp_slit')
temp_slit.caption = "The AIA maps were processed into temperature maps, and a slit was taken at the half height, perpendicular to the axis of evolution. The temperature maps were taken for the time over which the second acceleration of material occured. The colorbar indicates the passage of time and the various lines applicable to the slits is demonstrated."
temp_slit = manager.save_figure('temp_slit')

>>>>

fig = plt.figure(figsize=texfigure.figsize(pytex))
plt.imshow(np.rot90(data[2])[::-1, 100:], cmap='viridis', aspect='auto', origin='lower', norm=norm)
plt.colorbar()
plt.xlabel('Time in SST cadence (7.7 s)')
plt.ylabel('Distance along the slit')
sst_slit_fig = manager.save_figure('sst-slit', fig)
sst_slit_fig.figure_env_name = r'figure*'
sst_slit_fig.figure_width = r'\columnwidth'
sst_slit_fig.placement = 't'
sst_slit_fig.caption = r'CRISP/SST H$\alpha$ core line slit analysis.'

@@

dops = np.zeros((len(dop_files), 331, 120))
for i, afile in enumerate(dop_files):
    dops[i] = np.load(afile)

@@

fig, ax = plt.subplots(figsize=texfigure.figsize(pytex, reference='temp-slit'))
temp_slit = texfigure.Figure(fig, reference='temp_slit')
temp_slit.caption = "The AIA maps were processed into temperature maps, and a slit was taken at the half height, perpendicular to the axis of evolution. The temperature maps were taken for the time over which the second acceleration of material occured. The colorbar indicates the passage of time and the various lines applicable to the slits is demonstrated."
temp_slit = manager.save_figure('temp_slit')
